---
title: "Resilience Atttribute Case by Case Comparison"
author: "Meghan Fletcher"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load libraries
library(ggplot2)
library(tidyverse)
library(janitor)
library(googlesheets4)
library(here)
```

# Read in the data from Google Sheets
```{r}
aguion_barnacle <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1WfGsKOT0gFSN1yHUObDNSQflqd5avodSuf3kOZLTyLk/edit#gid=1947230832", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "aguion",
             reference = "aguion1",
             .after = "question_id")



#######################################################################################################################
#burden_sardine <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1umFwY33PSTJYmlfSIZiIWmT2gIBQeYCw/edit?usp=drive_web&ouid=1082#97509896161547373&rtpof=true", 
#                           sheet = "UPDATED_S4_ResilienceAttributes",
#                           range = "A6:P61",
#                           col_names = TRUE,
#                           na = "",
#                           guess_max = 10000,
#                           trim_ws = TRUE,
#                           col_types = "c"
#                           ) %>%
#  as_tibble() %>%
#  clean_names()%>% 
#  add_column(case_study = "burden",
#             reference = "burden1",
#             .after = "question_id")



#######################################################################################################################
dickey_collas_eur <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1hfXTM5hwe0iLWQQmrc31-xruOV3SUixuxqRSuqC8ydA/edit#gid=1707192308", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "dickey_collas",
             reference = "dickey_collas1",
             .after = "question_id")



#######################################################################################################################
eurich_clam <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1ZEIev1lcoD6Lxu3otzDCfbJJSiPJoZeyYbTvBXb_S9U/edit#gid=1453404713", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "eurich",
             reference = "eurich1",
             .after = "question_id")



#####################################################################################################################################
free_crab <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/12zMb5el0QAB-CdZdmdKjWw5Krbwx7farqlUvbN08HEg/edit#gid=390317686", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "free",
             reference = "free1",
             .after = "question_id")



#######################################################################################################################
#golden_madagascar <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1w99nN8C_Vd82j4Y23g2ZG_kuEh_Jc2HkW6lnLkhzeCU/edit#gid=1980661832", 
#                           sheet = "UPDATED_S4_ResilienceAttributes",
#                           range = "A6:P61",
#                           col_names = TRUE,
#                           na = "",
#                           guess_max = 10000,
#                           trim_ws = TRUE,
#                           col_types = "c"
#                           ) %>%
#  as_tibble() %>%
#  clean_names() %>% 
#  add_column(case_study = "golden",
#             reference = "golden1",
#             .after = "question_id")



#######################################################################################################################
friedman_fiji <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/13fgkP1xHZB6gZqXUBHuylaC3ImCDIDTFFjqQ8RAoV-s/edit#gid=476628697", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "friedman",
             reference = "friedman1",
             .after = "question_id")



#######################################################################################################################
hollowed_bering_sea <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1YOYZ9T7RR_8OkqQIWeZobhS-3yaEbKmuAVz16Nrrz9g/edit#gid=1980661832", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "hollowed",
             reference = "hollowed1",
             .after = "question_id")



########################################################################################################################
kisara_squid <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1RX1iUmEKsOUmuPZkn4SMA6zts9TTPz-gi0D6XFrY1RQ/edit#gid=934077877", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "kisara",
             reference = "kisara1",
             .after = "question_id") 



###########################################################################################################################
kleisner_jfi <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1YM1wc6F0SgGIoBcTvSjVyLJquE6-6Chk1dPFoLiXuQY/edit#gid=1865610127", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "kleisner",
             reference = "kleisner1",
             .after = "question_id")



################################################################################################################################
lau_png <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/18po7Pgq5Od6Q8yCnFdSfj_Gaxii34e-WsYwBFA3RTvo/edit#gid=1980661832", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "lau",
             reference = "lau1",
             .after = "question_id")



###############################################################################################################################
mason_iceland <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1ZPs5ow4wpZgj5eP26jvoMRgD9q6VT9DEdkJfqj7UrRE/edit#gid=2142384281", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "mason",
             reference = "mason1",
             .after = "question_id")




##########################################################################################################################
mills_lobster <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1HEPT54TsR1aTNNzDtZI59zU0eb-eJfH61ujErxAFtiI/edit#gid=553950990", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "mills",
             reference = "mills1",
             .after = "question_id")



########################################################################################################################
pecl_lobster <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/11Z-SLlAS0f9Ug1Z8gLMnHkaN7hoZT1W0KMVLG8HtbXs/edit#gid=179679195", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "pecl",
             reference = "pecl1",
             .after = "question_id")



###########################################################################################################################
#schmidt_senegal <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1bUY6yII5y0FZfDRJ5lxpA7iD2p3o__2A1xsWivxwKB0/edit#gid=2000123802", 
#                           sheet = "UPDATED_S4_ResilienceAttributes",
#                           range = "A6:P61",
#                           col_names = TRUE,
#                           na = "",
#                           guess_max = 10000,
#                           trim_ws = TRUE,
#                           col_types = "c"
#                           ) %>%
#  as_tibble() %>%
#  clean_names() %>% 
#  add_column(case_study = "schmidt",
#             reference = "schmidt1",
#             .after = "question_id") 



###############################################################################################################################
tokunaga_lobster <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1jgFZut693B14rdKbxprKtQcoh-mFlMzAktekjhvwf2Q/edit#gid=228934601", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "tokunaga",
             reference = "tokunaga1",
             .after = "question_id") 



############################################################################################################################
westfall_hms <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1DMx0Ux9Li1LhIe4ee5bbAYtJaw1vCezziRGyeERBthY/edit#gid=1818956842", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "westfall",
             reference = "westfall1",
             .after = "question_id")



###################################################################################################################################
zhao_moorea <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1-Muz76--fNv1qfdXZcBENP-agemTTySZAay9uAEO0HI/edit#gid=1980661832", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "zhao",
             reference = "zhao1",
             .after = "question_id")
```


# Merge the datasets

```{r}
attributes_merged <- rbind(aguion_barnacle, dickey_collas_eur, eurich_clam, free_crab, friedman_fiji, hollowed_bering_sea, kleisner_jfi, lau_png, mason_iceland, mills_lobster, pecl_lobster, tokunaga_lobster, westfall_hms, zhao_moorea)


# Data frames that don't bind:
#  kisara_squid

```



# Clean the merged datasets 

```{r}
attributes_merged_clean <- attributes_merged %>% 
  rename(dimension=dimensions, 
         domain=new_domain, 
         attribute=resilience_attribute, 
         score=score_1_4,
         quality=information_quality, 
         importance=importance_of_attribute_in_study_system_high_medium_low, 
         work_as_described=does_the_mechanism_work_as_described_in_this_fishery_system) %>% 
# Simplify
  select(dimension, domain, case_study, reference, attribute, score, quality, importance, work_as_described) %>% 
# Remove spacer rows
  filter(!is.na(attribute)) %>% 
# Format scores
  filter(!is.na(score)) %>% 
# In order to get rid of "NA" values that were purposefully entered into the data, I used the `case_when` function to revert
  mutate(official_score = case_when(
    score == "1" ~ "1",
    score == "2" ~ "2",
    score == "3" ~ "3",
    score == "4" ~ "4",
    score == "NA" ~ "0"
  )) %>% 
  mutate(official_score=as.numeric(official_score)) %>%
  # Formate dimension
  mutate(dimension=recode_factor(dimension, 
                                 "Ecological"="Ecological",
                                 "Socio-economic"="Social-economic",
                                 "Governance-management"="Goverance")) %>% 
# Format data quality
  mutate(quality=ifelse(quality=="NA - Not relevant in this system", NA, quality),
         quality=recode_factor(quality,
                               "E - No data"="No data", ### CF used "E - No data/information; no basis for expert judgement", but JE's was different
                               "D - not confident that the answer provided reflects the true state of the system"="Low",
                               "C - fairly confident that the answer provided reflects the true state of the system"="Fair",
                               "B - limited data/information and expert judgement"="Good",
                               "A - adequate and reliable data/information"="Excellent")) %>% 
  # Format importance
  mutate(importance=stringr::str_to_sentence(importance),
         importance=factor(importance, levels=c("Low", "Medium", "High")))   
  
```

```{r}
#%>% 
  # Arrange
  # arrange(dimension, domain, official_score)%>% 
  # Set attribute order
  #mutate(attribute=factor(attribute, levels=attribute))
  # Format attribute - to put an * next to the attribute name is the `work_as_described` column says "no"
  #mutate(attribute=ifelse(work_as_described=="no", paste0(attribute, "*"), attribute)) 

# To remove the astrisks if added back into the dataset:
#aguion1 <- aguion_barnacle %>% 
  #select(attribute, score) %>% 
  #mutate(attribute = gsub("\\*", "", attribute))
```


# Plot the merged data by attribute of interest


```{r}
# Create theme
my_theme <-  theme(axis.text=element_text(size=8),
                   axis.title=element_text(size=9),
                   legend.text=element_text(size=8),
                   legend.title=element_text(size=9),
                   strip.text=element_text(size=9),
                   plot.title=element_text(size=10),
                   # Gridlines
                   panel.grid.major = element_blank(), 
                   panel.grid.minor = element_blank(),
                   panel.background = element_rect(fill = "black"), 
                   axis.line = element_line(colour = "black"))
```

## Ecological

### Assets
#### Population Abundance
```{r}
# Filter the data to get the attribute you're looking for
population_abundance <- attributes_merged_clean %>% 
  filter(attribute == "Population abundance") 

ggplot(population_abundance, aes(x = case_study, y = official_score)) +
  geom_bar(stat = 'identity') +
  labs(title = "Population Abundance Scores Across Case Studies", x = "Case Studies", y = "Attribute Score")
```

#### Age Structure

```{r}

```


#### Genetic Diversity

```{r}

```


#### Species Diversity

```{r}

```


### Flexibility
#### Adult Mobility

```{r}

```


#### Larval Dispersal

```{r}

```


#### Environmental Niche Breadth

```{r}

```


#### Dietary Flexibility

```{r}

```


#### Habitat Diversity

```{r}

```


#### Plasticity

```{r}

```


#### Evolutionary Potential

```{r}

```


### Organization
#### Ecosystem Connectivity

```{r}

```


#### Population Modularity

```{r}

```


## Socio-economic

### Assets
#### Wealth and Reserves

```{r}

```


#### Economic Diversity

```{r}

```


#### Social Diversity

```{r}

```


### Flexibility
#### Flexible and Agile Infrstructure

```{r}

```


#### Mobility

```{r}

```


#### Economic Opportunity

```{r}

```


#### Resilience Mindset

```{r}

```


#### Place Attachment

```{r}

```


### Orgaanization
#### Social Capital

```{r}

```


#### Technology Transfer

```{r}

```


#### Modular Infrastructure

```{r}

```


###
####



















