---
title: "Evaluating Data Quality Across Case Studies"
author: "Meghan Fletcher"
date: "2/1/2022"
output: 
  html_document:
    theme: flatly
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE, message = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

#Load libraries
library(ggplot2)
library(tidyverse)
library(janitor)
library(googlesheets4)
library(here)
library(kableExtra)
```


# Read in the data from Google Sheets
```{r, results=FALSE, message = FALSE, warning = FALSE, class.source = 'fold-hide', warning = FALSE}
aguion_barnacle <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1WfGsKOT0gFSN1yHUObDNSQflqd5avodSuf3kOZLTyLk/edit#gid=1947230832", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Aguion",
             reference = "aguion1",
             .after = "question_id")


#######################################################################################################################
burden_sardine <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1TkB-P94xgRssmcbAuzwoh0BlDdvUfYHO7vWjK6r2pxs/edit#gid=1965519914", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names()%>% 
  add_column(case_study = "Burden",
             reference = "burden1",
             .after = "question_id")



#######################################################################################################################
dickey_collas_eur <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1hfXTM5hwe0iLWQQmrc31-xruOV3SUixuxqRSuqC8ydA/edit#gid=1707192308", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Dickey_Collas",
             reference = "dickey_collas1",
             .after = "question_id")



#######################################################################################################################
eurich_clam <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1ZEIev1lcoD6Lxu3otzDCfbJJSiPJoZeyYbTvBXb_S9U/edit#gid=1453404713", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Eurich",
             reference = "eurich1",
             .after = "question_id")



#####################################################################################################################################
free_crab <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/12zMb5el0QAB-CdZdmdKjWw5Krbwx7farqlUvbN08HEg/edit#gid=390317686", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Free",
             reference = "free1",
             .after = "question_id")



#######################################################################################################################
golden_madagascar <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1w99nN8C_Vd82j4Y23g2ZG_kuEh_Jc2HkW6lnLkhzeCU/edit#gid=390607640", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Golden",
             reference = "golden1",
             .after = "question_id")



#######################################################################################################################
friedman_fiji <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/13fgkP1xHZB6gZqXUBHuylaC3ImCDIDTFFjqQ8RAoV-s/edit#gid=476628697", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Friedman",
             reference = "friedman1",
             .after = "question_id")



#######################################################################################################################
hollowed_bering_sea <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1YOYZ9T7RR_8OkqQIWeZobhS-3yaEbKmuAVz16Nrrz9g/edit#gid=9514874", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Hollowed",
             reference = "hollowed1",
             .after = "question_id")



########################################################################################################################
kisara_squid <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1RX1iUmEKsOUmuPZkn4SMA6zts9TTPz-gi0D6XFrY1RQ/edit#gid=934077877", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Kisara",
             reference = "kisara1",
             .after = "question_id") 



###########################################################################################################################
kleisner_jfi <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1YM1wc6F0SgGIoBcTvSjVyLJquE6-6Chk1dPFoLiXuQY/edit#gid=1865610127", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Kleisner",
             reference = "kleisner1",
             .after = "question_id")



################################################################################################################################
lau_png <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/18po7Pgq5Od6Q8yCnFdSfj_Gaxii34e-WsYwBFA3RTvo/edit#gid=1980661832", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Lau",
             reference = "lau1",
             .after = "question_id")



###############################################################################################################################
mason_iceland <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1ZPs5ow4wpZgj5eP26jvoMRgD9q6VT9DEdkJfqj7UrRE/edit#gid=2142384281", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Mason",
             reference = "mason1",
             .after = "question_id")




##########################################################################################################################
mills_lobster <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1HEPT54TsR1aTNNzDtZI59zU0eb-eJfH61ujErxAFtiI/edit#gid=553950990", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Mills",
             reference = "mills1",
             .after = "question_id")



########################################################################################################################
pecl_lobster <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/11Z-SLlAS0f9Ug1Z8gLMnHkaN7hoZT1W0KMVLG8HtbXs/edit#gid=179679195", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Pecl",
             reference = "pecl1",
             .after = "question_id")



###########################################################################################################################
#schmidt_senegal <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1bUY6yII5y0FZfDRJ5lxpA7iD2p3o__2A1xsWivxwKB0/edit#gid=2000123802", 
#                           sheet = "UPDATED_S4_ResilienceAttributes",
#                           range = "A6:P61",
#                           col_names = TRUE,
#                           na = "",
#                           guess_max = 10000,
#                           trim_ws = TRUE,
#                           col_types = "c"
#                           ) %>%
#  as_tibble() %>%
#  clean_names() %>% 
#  add_column(case_study = "Schmidt",
#             reference = "schmidt1",
#             .after = "question_id") 



###############################################################################################################################
tokunaga_lobster <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1jgFZut693B14rdKbxprKtQcoh-mFlMzAktekjhvwf2Q/edit#gid=228934601", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Tokunaga",
             reference = "tokunaga1",
             .after = "question_id") 



############################################################################################################################
westfall_hms <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1DMx0Ux9Li1LhIe4ee5bbAYtJaw1vCezziRGyeERBthY/edit#gid=1818956842", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Westfall",
             reference = "westfall1",
             .after = "question_id")



###################################################################################################################################
zhao_moorea <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1-Muz76--fNv1qfdXZcBENP-agemTTySZAay9uAEO0HI/edit#gid=1980661832", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Zhao",
             reference = "zhao1",
             .after = "question_id")
```


##############################################################################################

# Merge the datasets

```{r}
attributes_merged <- rbind(aguion_barnacle, burden_sardine, dickey_collas_eur, eurich_clam, free_crab, friedman_fiji, golden_madagascar, hollowed_bering_sea, kisara_squid, kleisner_jfi, lau_png, mason_iceland, mills_lobster, pecl_lobster, tokunaga_lobster, westfall_hms, zhao_moorea)

```


# Clean the merged datasets 

```{r}
attributes_merged_clean <- attributes_merged %>% 
  rename(dimension=dimensions, 
         domain=new_domain, 
         attribute=resilience_attribute, 
         score=score_1_4,
         quality=information_quality, 
         importance=importance_of_attribute_in_study_system_high_medium_low, 
         work_as_described=does_the_mechanism_work_as_described_in_this_fishery_system) %>% 
# Simplify
  select(dimension, domain, case_study, reference, attribute, score, quality, importance, work_as_described) %>% 
# Remove spacer rows
  filter(!is.na(attribute)) %>% 
# Format scores
  filter(!is.na(score)) %>% 
# In order to get rid of "NA" values that were purposefully entered into the data, I used the `case_when` function to revert
  mutate(official_score = case_when(
    score == "1" ~ "1",
    score == "2" ~ "2",
    score == "3" ~ "3",
    score == "4" ~ "4",
    score == "NA" ~ "0"
  )) %>% 
  mutate(official_score=as.numeric(official_score)) %>%
  # Formate dimension
  mutate(dimension=recode_factor(dimension, 
                                 "Ecological"="Ecological",
                                 "Socio-economic"="Social-economic",
                                 "Governance-management"="Goverance")) %>% 
# Format data quality
  mutate(quality=ifelse(quality=="NA - Not relevant in this system", NA, quality),
         quality=recode_factor(quality,
                               "E - No data/information; no basis for expert judgement"="No data", ### CF used "E - No data/information; no basis for expert judgement", but JE's was different
                               "D - not confident that the answer provided reflects the true state of the system"="Low",
                               "C - fairly confident that the answer provided reflects the true state of the system"="Fair",
                               "B - limited data/information and expert judgement"="Good",
                               "A - adequate and reliable data/information"="Excellent")) %>% 
  # To fix some errors around data quality in the original datasets
  mutate(quality=recode_factor(quality,
                               "E - No data"="No data")) %>% 
  # Create a new column to house numeric values for information quality
  mutate(numeric_quality = case_when(
    quality == "Excellent" ~ 4,
    quality == "Good" ~ 3,
    quality == "Fair" ~ 2,
    quality == "Low" ~ 1,
    quality == "No data" ~ 0)) %>% 
  filter(!is.na(numeric_quality)) %>% 
  # Format importance
  mutate(importance=stringr::str_to_sentence(importance),
         importance=factor(importance, levels=c("Low", "Medium", "High"))) %>% 
  # Create a new column to house numeric values for importance
  mutate(numeric_importance = case_when(
    importance == "Low" ~ "1",
    importance == "Medium" ~ "2",
    importance == "High" ~ "3")) %>% 
  mutate(numeric_importance=as.numeric(numeric_importance)) %>% 
  filter(!is.na(numeric_importance))
  

```


################################################################################################

# Find Data Quality Score Means 
The data quality score means of each attribute are reflected in the table. These means are based off of all case studies combined. In order to calculate the means of each attribute, the data quality levels needed to converted to numeric values so, _Excellent = 4, Good = 3, Fair = 2, Low = 1, and No data = 0_.

```{r}
# Build a table
merged_quality <- attributes_merged_clean %>% 
  group_by(attribute) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  mutate(across(where(is.numeric), ~ round(., 3)))

# Use `kableExtra` package to create table
merged_quality %>% 
  kbl(caption = "Data Quality Means by Attribute") %>% 
   kable_classic_2(full_width = F, html_font = "Cambria") %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Data quality means by dimension

```{r}
# Find means across domains but within each dimension
dimension_quality <- attributes_merged_clean %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list("Mean" = mean, "Standard Deviaton" = sd)) %>% 
  rename(Dimension = dimension) %>% 
  mutate(across(where(is.numeric), ~ round(., 3)))

# Create a table
dimension_quality %>% 
  kbl(caption = "Data Quality Means by Dimension") %>% 
   kable_classic_2(full_width = F, html_font = "Cambria") %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Data quality means by domain

```{r}
# Find means across domains but within each dimension
domain_quality <- attributes_merged_clean %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  mutate(across(where(is.numeric), ~ round(., 2)))

# Create a table
domain_quality %>% 
  kbl(caption = "Data Quality Means by Domain") %>% 
   kable_classic_2(full_width = F, html_font = "Cambria") %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```



##############################################################################################

# Grouping Data Quality Stats

## Data Quality Means by Dimension
```{r}
# Create a table where the average scores of each domain across case studies are represented

# Aguion mean
aguion_dim <- attributes_merged_clean %>% 
  filter(case_study == "Aguion") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Aguion = data_quality,
         Dimension=dimension)

# Burden hasn't filled in this column yet
# Burden mean
#burden_dim <- attributes_merged_clean %>% 
#  filter(case_study == "Burden") %>% 
#  group_by(dimension) %>% 
#  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
#  rename(Burden = data_quality)  

# Dickey-Collas mean
dickey_collas_dim <- attributes_merged_clean %>% 
  filter(case_study == "Dickey_Collas") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Dickey_Collas = data_quality)  

# Eurich mean
eurich_dim <- attributes_merged_clean %>% 
  filter(case_study == "Eurich") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Eurich = data_quality) 

# Free mean
free_dim <- attributes_merged_clean %>% 
  filter(case_study == "Free") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Free = data_quality) 

# Friedman mean
friedman_dim <- attributes_merged_clean %>% 
  filter(case_study == "Friedman") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Friedman = data_quality) 

# Golden mean
golden_dim <- attributes_merged_clean %>% 
  filter(case_study == "Golden") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Golden = data_quality) 

# Hollowed mean
hollowed_dim <- attributes_merged_clean %>% 
  filter(case_study == "Hollowed") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Hollowed = data_quality) 

# Kisara mean
kisara_dim <- attributes_merged_clean %>% 
  filter(case_study == "Kisara") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Kisara = data_quality) 

# Kleisner mean
kleisner_dim <- attributes_merged_clean %>% 
  filter(case_study == "Kleisner") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Kleisner = data_quality) 

# Lau mean
lau_dim <- attributes_merged_clean %>% 
  filter(case_study == "Lau") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Lau = data_quality) 

# Mason mean
mason_dim <- attributes_merged_clean %>% 
  filter(case_study == "Mason") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Mason = data_quality) 

# Mills mean
mills_dim <- attributes_merged_clean %>% 
  filter(case_study == "Mills") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Mills = data_quality) 

# Pecl mean
pecl_dim <- attributes_merged_clean %>% 
  filter(case_study == "Pecl") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Pecl = data_quality) 

# Tokunaga mean
tokunaga_dim <- attributes_merged_clean %>% 
  filter(case_study == "Tokunaga") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Tokunaga = data_quality) 

# Westfall mean
westfall_dim <- attributes_merged_clean %>% 
  filter(case_study == "Westfall") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Westfall = data_quality) 

# Zhao mean
zhao_dim <- attributes_merged_clean %>% 
  filter(case_study == "Zhao") %>% 
  group_by(dimension) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Zhao = data_quality)
```

```{r}
### Kisara Case Study missing b/c no information forsome of the dimensions 

# Merge all mean datasets together
dimension_quality_merged <- cbind(aguion_dim, dickey_collas_dim, eurich_dim, free_dim, friedman_dim, golden_dim, hollowed_dim,  kleisner_dim, lau_dim, mason_dim, mills_dim, pecl_dim, tokunaga_dim, westfall_dim, zhao_dim) %>% 
  select(Dimension, Aguion, Dickey_Collas, Eurich, Free, Friedman, Golden, Hollowed, Kleisner, Lau, Mason, Mills, Pecl, Tokunaga, Westfall, Zhao) %>% 
  mutate(across(where(is.numeric), ~ round(., 2)))


# Create a table
dimension_quality_merged %>% 
  kbl(caption = "Data Quality Means Across Case Studies by Dimension") %>% 
   kable_classic_2(full_width = F, html_font = "Cambria") %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


## Data Quality Means by Domain

```{r}
# Create a table where the average data quality scores of each domain across case studies are represented

# Aguion mean
aguion_dom <- attributes_merged_clean %>% 
  filter(case_study == "Aguion") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Aguion = data_quality) 

# Burden mean
#burden_dom <- attributes_merged_clean %>% 
#  filter(case_study == "Burden") %>% 
#  group_by(dimension, domain) %>% 
#  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
#  rename(Burden = data_quality)

# Dickey-Collas mean
dickey_collas_dom <- attributes_merged_clean %>% 
  filter(case_study == "Dickey_Collas") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Dickey_Collas = data_quality) 

# Eurich mean
eurich_dom <- attributes_merged_clean %>% 
  filter(case_study == "Eurich") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Eurich = data_quality)

# Free mean
free_dom <- attributes_merged_clean %>% 
  filter(case_study == "Free") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Free = data_quality)

# Friedman mean
friedman_dom <- attributes_merged_clean %>% 
  filter(case_study == "Friedman") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Friedman = data_quality)

# Golden Mean
golden_dom <- attributes_merged_clean %>% 
  filter(case_study == "Golden") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Golden = data_quality)

# Hollowed mean
hollowed_dom <- attributes_merged_clean %>% 
  filter(case_study == "Hollowed") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Hollowed = data_quality)

# Kisara mean
kisara_dom <- attributes_merged_clean %>% 
  filter(case_study == "Kisara") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Kisara = data_quality)

# Kleisner mean
kleisner_dom <- attributes_merged_clean %>% 
  filter(case_study == "Kleisner") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Kleisner = data_quality)

# Lau mean
lau_dom <- attributes_merged_clean %>% 
  filter(case_study == "Lau") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Lau = data_quality)

# Mason mean
mason_dom <- attributes_merged_clean %>% 
  filter(case_study == "Mason") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Mason = data_quality)

# Mills mean
mills_dom <- attributes_merged_clean %>% 
  filter(case_study == "Mills") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Mills = data_quality)

# Pecl mean
pecl_dom <- attributes_merged_clean %>% 
  filter(case_study == "Pecl") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Pecl = data_quality)

# Tokunaga mean
tokunaga_dom <- attributes_merged_clean %>% 
  filter(case_study == "Tokunaga") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Tokunaga = data_quality)

# Westfall mean
westfall_dom <- attributes_merged_clean %>% 
  filter(case_study == "Westfall") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Westfall = data_quality)

# Zhao mean
zhao_dom <- attributes_merged_clean %>% 
  filter(case_study == "Zhao") %>% 
  group_by(dimension, domain) %>% 
  summarise_at(vars(numeric_quality), list(data_quality = mean)) %>% 
  rename(Zhao = data_quality)
```

```{r}
### Kisara Case Study missing b/c no information for some of the dimensions 
#### Burden has not filled this section in

# Merge all mean datasets together
means_merged_by_case <- cbind(aguion_dom, dickey_collas_dom, eurich_dom, free_dom, friedman_dom, golden_dom, hollowed_dom,  kleisner_dom, lau_dom, mason_dom, mills_dom, pecl_dom, tokunaga_dom, westfall_dom, zhao_dom) %>% 
  select(dimension...1, domain...2, Aguion, Dickey_Collas, Eurich, Free, Friedman, Golden, Hollowed, Kleisner, Lau, Mason, Mills, Pecl, Tokunaga, Westfall, Zhao) %>% 
  rename(Dimension = dimension...1, Domain = domain...2) %>% 
  mutate(across(where(is.numeric), ~ round(., 2)))

# Create a table
means_merged_by_case %>% 
  kbl(caption = "Data Quality Means Across Case Studies") %>% 
   kable_classic_2(full_width = F, html_font = "Cambria") %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

####################################################################################################

# Visualize Data Quality Means

```{r}
# Create theme
my_theme <-  theme(axis.text.x=element_text(size=7, angle=38, hjust=0.8),
                   axis.text.y=element_text(size=8),
                   legend.text=element_text(size=8),
                   legend.title=element_text(size=9),
                   strip.text=element_text(size=9),
                   # Gridlines
                   panel.grid.major = element_blank(), 
                   panel.grid.minor = element_blank(),
                   panel.background = element_rect(), 
                   axis.line = element_line())
```

```{r}
# Bar graph showing average comparison by dimension across case studies

dimension_comparison <- dimension_quality_merged %>% 
  pivot_longer(!Dimension, names_to = "case_study", values_to = "means") %>% 
  mutate(across(where(is.numeric), ~ round(., 2)))


ggplot(dimension_comparison, aes(x = case_study, y = means, fill = Dimension)) +
  geom_bar(stat="identity", width=0.7, position=position_dodge(width=1)) +
  theme_bw() + my_theme +
  facet_wrap(~Dimension, scales = "free_x") +
  theme(legend.position="top") +
  scale_fill_brewer(palette = "Accent") +
  geom_hline(data=dimension_quality, aes(yintercept = (Mean)), linetype="dashed", colour="black") +
  labs(x = "Case Studies", y = "Data Quality Averages")
```

```{r}
# Make a stacked graph for the data

quality_stacked <- ggplot(dimension_comparison, aes(x = case_study, y = means, fill = Dimension, label = means)) +
  geom_bar(stat="identity", position="stack") +
  theme_bw() + my_theme +
  theme(legend.position="top") +
  labs(x = "Case Studies", y = "Attribute Score Averages") +
  scale_fill_brewer(palette = "Accent") +
  geom_text(size = 3, position = position_stack(vjust = 0.5))
plot(quality_stacked)
```


##################################################################################################

# Importance Score Proportions

```{r}
# Create a table that shows the counts and proportions of attribute scores to help identify which are scoring higher than others and vice versa.

quality_stats <- attributes_merged_clean %>% 
  select(dimension, quality) %>% 
  tabyl(dimension,quality) %>%
  adorn_percentages() %>% 
  adorn_pct_formatting(digits = 2) %>% 
  column_to_rownames(var = "dimension")


# Create a table
quality_stats %>% 
  kbl(caption = "Proportion of Data Quality Levels by Dimension") %>% 
   kable_classic_2(full_width = F, html_font = "Cambria") %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


